% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author)
% http://mboedick.org (c) 2003-2007 David J. Grant
% <davidgrant-at-gmail.com> http://www.davidgrant.ca (c) 2008-2015
% Nathaniel Johnston <nathaniel@njohnston.ca> http://www.njohnston.ca
% This work is licensed under the Creative Commons
% Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of
% this license, visit
% http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter
% to Creative Commons, 543 Howard Street, 5th Floor, San Francisco,
% California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{hyperref}

% The following two lines are needed to fix a MacTex compatibility issue
% Thanks to Tony Blake for finding this fix!
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
% Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
% Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolor}{gray}{0.75}  
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars
\urlstyle{rm}

%-----------------------------------------------------------
% Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
      \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
	\textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}}
\newcommand{\olressubheading}[2]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
  \end{tabular*}}%\vspace{6pt}}
\newcommand{\leftsubheading}[1]{
  \textbf{#1\vspace{-6pt} \\}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Gregory Davidson} & \textbf{\today} \\
  Senior Research and Development Staff &
  (865) 574-3921 \\
  Reactor and Nuclear Systems Division &
  \href{mailto:davidsongg@ornl.gov}{davidsongg@ornl.gov} \\
  Oak Ridge National Laboratory &
  \url{https://www.ornl.gov/staff-profile/gregory-g-davidson} \\  
  1 Bethel Valley Rd. & \\
  Oak Ridge, TN  37831 & \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{center}
    \parbox{6.762in}{My research interests include deterministic
      transport algorithms, such as finite element SN discretizations
      and time differencing methods, Monte Carlo transport,
      sensitivity/uncertainty analysis, discrete diffusion Monte Carlo
      methods, multiphysics methods, transport-depletion coupling
      methods, hydrodynamics, software engineering, object-oriented
      programming, programming for massively-parallel systems,
      especially leadership-class computing, and programming for
      heterogeneous architectures.}
  \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
  \ressubheading{University of Michigan}{Ann Arbor,
    MI}{Ph.D. Nuclear Engineering and Radiological Sciences and
    Scientific Computing}{2004 - 2009}
  \begin{itemize}
	\resitem{Dissertation: Time-Dependent Radiation Transport
      using the Staggered-Block Jacobi Method}
	\resitem{GPA: 8.15/9.00}
  \end{itemize}

\item
  \ressubheading{Oregon State University}{Corvallis, OR}{M.S. Nuclear
    Engineering}{2002 - 2004}
	\begin{itemize}
	  \resitem{Thesis: Finite Element Transport using Wachspress
        Rational Basis Functions on Quadrilaterals in Diffusive Regions}
		\resitem{GPA: 3.93 / 4.00}
	\end{itemize}

\item
  \ressubheading{Oregon State University}{Corvallis, OR}{Honor's
    B.S. Nuclear Engineering}{1998 - 2002}
	\begin{itemize}
	  \resitem{Undergraduate Thesis: Finite Element Diffusion
        Solutions on Arbitrary Quadrilaterals using Wachspress
        Rational Functions}
		\resitem{GPA: 3.94 / 4.00}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
  \olressubheading{Oak Ridge National Laboratory}{2009 - Present}
  Research and development associate as part of the Shift/Denovo team,
  investigating advanced, massively parallel radiation transport
  solutions, including both fixed-source and k-eigenvalue problems, as
  well as transport-depletion coupling schemes.  Also part of the
  development team of CASL as a member of the VERA-RTM area.  Have
  worked extensively in multicode coupling, including coupling to the
  XSProc package in Scale for automated cross-section generation,
  coupling to ORIGEN for depletion calculations, and to the AMP
  (Advanced MultiPhysics) fuel performance code.

\item
  \olressubheading{Los Alamos National Laboratory}{Summer 2005}
  Implemented an emissivity-preserving discrete diffusion Monte Carlo
  (DDMC) transport scheme in C++.  Wrote and tested the
  asymptotically-correct angular distribution functionality for
  transport-diffusion interfaces in DDMC methods.

\item
  \olressubheading{Bettis Atomic Power Laboratory}{Summer 2003}
  Derived the equations for the constant-constant, constant-linear,
  and linear-linear short characteristics methods on rectangular
  zones.  Wrote the constant-linear characteristics method into an
  existing SN code in Fortran 90.

\item
  \olressubheading{Lawrence Livermore National Laboratory}{Summer
    2002}
  Researched a finite-element transport method using Wachspress
  rational basis functions for solving the  discrete-ordinates neutron
  transport equation. 

\item
  \olressubheading{Lawrence Livermore National Laboratory}{Summer
    2001}
  Investigated a one-dimensional computational hydrodynamics scheme
  based on rational basis functions.

\item
  \olressubheading{Lawrence Livermore National Laboratory}{Summer
    2000}
  Implemented relativistic fluid motion corrections and momentum
  deposition into the particle Monte Carlo package of Kull, a
  three-dimensional multiphysics code, in C++ and Python. 
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Honors and Awards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item R\&D100 Award for the Virtual Environment for Reactor
  Applications (VERA) reactor simulator code.
\item 2014 ORNL Engineering Research and Development team award
\item Principle Investigator of the ORNL LDRD, "Advanced Modeling \&
  Simulation to Support High Performance Research Reactor Conversions
  to Low Enriched Uranium"
\item Principle Investigator of the ASCR Leadership Computing
  Challenge, "Advanced Simulation of HFIR for LEU Conversion"
\item Awarded the HPC Innovation Excellence Award
\item 2012 Oak Ridge National Laboratory Significant Event Award
\item 2011 MeV Summer School: Best Technical Paper Award
\item American Nuclear Society, Mathematics and Computation
  Division, Best Paper and Presentation Award, November 2010
\item 2010 ORNL Engineering Research and Development team award
\item D.O.E. Computational Science Graduate Fellowship Award
\item Master's Thesis of the Year, Nuclear Engineering
  Department, Oregon State University
\item Honor's College Member at Oregon State University
\item Tau Beta Pi Engineering Honor Society
\item Phi Kappa Phi Honor Society
\item Alpha Lambda Delta Honorary Fraternity
\item National Academy for Nuclear Training Scholarship
\item Oregon Space Grant Scholarship
\item D.O.E. NEHP Scholarship
\item OSU Achievement Scholarship
\item Schuette Engineering Scholarship
\item Leo Adler Foundation Scholarship
\item Sanford Adler Scholarship
\item Nadie Strayer Scholarship
\item Grant-Baker Federal Credit Union Scholarship
\item Elks Scholarship
\end{itemize}  


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Journal Publications}
\begin{enumerate}
  \item Cihangir Celik, Douglas E. Peplow, Gregory G. Davidson, and
    Mathew R. Swinney, ``A Directional Detector Response Function for
    Anisotropic Detectors,'' Nucl. Sci. Eng. (in review).
  \item Douglas E. Peplow, Kaushik Banerjee, Gregory G. Davidson, Ian
    R. Stewart, Mathew W. Swinney, and Jackson N. Wagner, ``Preliminary
    Validation of the Shift Monte Carlo Code for Fixed-Source
    Radiation Transport Problems,'' Nucl. Tech. (in review).
  \item Gregory G. Davidson, Tara M. Pandya, Seth R. Johnson, Thomas
    M. Evans, Aarno E. Isotalo, Cole A Gentry, and William
    A. Wieselquist, ``Nuclide depletion capabilities in the Shift Monte
    Carlo code,'' Ann. Nucl. Energy, 114, 259-276 (2018).
  \item Lei Jin, Kaushik Banerjee, Steven P. Hamilton, and Gregory
    G. Davidson, ``Improving Variance Estimation in Monte Carlo
    Eigenvalue Simulations,'' Ann. Nucl. Energy, 110, 692-708 (2017).
  \item A.D. Nicholson, I. Garishvili, D.E. Peplow, D.E. Archer,
    W.R. Ray, M.W. Swinnery, M.J. Willis, G.G. Davidson,
    S.L. Cleveland, B.W. Patton, D.E. Hornback, J.J. Peltz,
    M.S.L. McLean, A.A. Plionis, B.J. Quiter, and M.S. Bandstra,
    ``Multiagency Urban Seach Experiment Detector and Algorithm Test
    Bed,'' IEEE Trans. Nucl. Sci., 64, 7, 1689-1695 (2017).
  \item A.E. Isotalo, G.G. Davidson, T.M. Pandya, W.A. Wieselquist,
    and S.R. Johnson, ``Flux Renormalization in Constant Power Burnup
    Calculations,'' Ann. Nucl. Energy, 96, 148-157 (2016).
  \item S.P. Hamilton, T.M. Evans, G.G. Davidson, S.R. Johnson,
    T.M. Pandya, and A.T. Godfrey, ``Hot Zero Power Reactor
    Calculations Using the Insilico Code,'' J. Comp. Phys., 314,
    700-711 (2016).
  \item T.M. Pandya, S.R. Johnson, T.M. Evans, G.G. Davidson,
    S.P. Hamilton, and A.T. Godfrey, ``Capabilities, Implementation,
    and Benchmarking of Shift, a Massively Parallel Monte Carlo
    Radiation Transport Code,'' J. Comp. Phys., 308, 239-272 (2016).
  \item R.N. Slaybaugh, T.M. Evans, G.G. Davidson, and P.P.H. Wilson,
    ``Multigrid in Energy Preconditioner for Krylov Solvers,''
    J. Comp. Phys., 272, 405-419 (2013).
  \item G.G. Davidson, T.M. Evans, J.J. Jarrell, S.P. Hamilton,
    T.M. Pandya, and R.N. Slaybaugh, ``Massively Parallel,
    Three-Dimensional Transport Solutions for the k-Eigenvalue
    Problem,'' Nucl. Sci. Eng. 177, 111-125 (2014).
  \item J.J. Jarrell, A.T. Godfrey, T.M. Evans, and G.G. Davidson,
    ``Full Core Reactor Analysis: Running Denovo on Jaguar,''
    Nucl. Sci. Eng., 175, 283-291 (2013).
  \item G. Yesilyurt, K.T. Clarno, T.M. Evans, G.G. Davidson, and
    P.B. Fox, ``C5 Benchmark Problem with Discrete Ordinate Radiation
    Transport Code Denovo,'' Nucl. Tech. 176(2), 274-283 (2011).
  \item G. Davidson and T.S. Palmer, ``Finite Element Transport Using
    Wachspress Rational Functions on Quadrilaterals in Thick Diffusive
    Regions,'' Nucl. Sci. Eng., 159, 242 (2008). 
  \item J.D. Densmore, G. Davidson, and D.B. Carrington, ``Emmissivity
    of Discretized Diffusion Problems,'' Ann. Nucl. Energy, 33, (2006).
\end{enumerate}

\leftsubheading{Conference Proceedings}
\begin{enumerate}
  \item Peplow, D.E., Swinney, Mathew W., Davidson, Gregory G.,
    Nicholson, Andrew D., and Patton, Bruce W., ``Initial Modeling of
    Urban Search Measurements,'' American Nuclear Society Annual
    Meeting, June 11 – 15, Chicago, IL (2017).
  \item Gentry, C., Godfrey, A., Pandya, T., Davidson, G., and
    Franceschini, F., ``AP1000 Benchmarking of VERA Neutronics
    Toolset,'' M\&C 2017 – International Conference on Mathematics and
    Computational Methods Applied to Nuclear Science and Engineering,
    Jeju, Korea, April 16-20 (2017).
  \item G.G. Davidson, T.M. Pandya, A.E. Isotalo, S.R. Johnson,
    T.M. Evans, and W.A. Wieselquist, ``Nuclide Depletion Capabilities
    in the Shift Monte Carlo Code,'' PHYSOR 2016, May 1-5, Sun Valley,
    ID.
  \item T.M. Pandya, S.R. Johnson, G.G. Davidson, T.M. Evans, and
    S.P. Hamilton, ``Shift: A Massively Parallel Monte Carlo Radiation
    Transport Package,'' M\&C 2015, April 19-23, Nashville, TN.
  \item T.M. Evans, W. Joubert, S.P. Hamilton, S.R. Johnson,
    J.A. Turner, G.G. Davidson, and T.M. Pandya, ``Three-Dimensional
    Discrete Ordinates Reactor Assembly Calculations on GPUs,'' M\&C
    2015, April 19-23, Nashville, TN.
  \item R.N. Slaybaugh, T.M. Evans, G.G. Davidson, and P.P.H. Wilson,
    ``Rayleigh Quotient Iteration with a Multigrid in Energy
    Preconditioner for Massively Parallel Neutron Transport,'' M\&C
    2015, April 19-23, Nashville, TN.
  \item S. Palmtag, K. Clarno, G. Davidson, et. al., ''Coupled
    Neutronics and Thermal-Hydraulic Solution of a Full-Core PWR Using
    VERA-CS,'' PHYSOR 2014, Kyoto, Japan.
  \item J.J. Jarrell, T.M. Evans, and G.G. Davidson, ''Discrete
    Ordinate Quadrature Selection for Reactor-based Eigenvalue
    Problems,'' M\&C 2013, Sun Valley, ID May 5-9, 2013.
  \item S. Hamilton, K. Clarno, M. Berrill, T. Evans, G. Davidson,
    R. Lefebvre, and R. Sampath, ''Multiphysics Simulations for LWR
    Analysis,'' M\&C 2013, Sun Valley, ID, May 5-9, 2013.
  \item C.G. Baker, G.G. Davidson, T.M. Evans, S.P. Hamilton,
    J.J. Jarrell, and W. Joubert, ''High Performance Radiation
    Transport Simulations on TITAN,'' Supercomputing SC12, Salt Lake
    City, NV, Nov. 12-15, 2012.
  \item J.J. Jarrell, A.T. Godfrey, T.M. Evans, and G.G. Davidson,
    ''Full Core Reactor Analysis: Running Denovo on Titan,'' PHYSOR
    2012, Knoxville, TN, April 15-20. On CD-ROM, American Nuclear
    Society, LaGrange Park, IL, 2012.
  \item R.N. Slaybaugh, T.M. Evans, G.G. Davidson, and P.P.H. Wilson,
    ''Rayleigh Quotient Iteration in 3D, Deterministic Neutron
    Transport,'' PHYSOR 2012, Knoxville TN, April 15-20.  On CD-ROM,
    American Nuclear Society, LaGrange, Park, IL, 2012.
  \item B. Vacaliuc, D.R. Patlolla, E. D'Avezado, G.G. Davidson,
    et. al., ''Python for Development of OpenMP and CUDA Kernals for
    Multidimensional Data,'' 2011 Symposium on Application Accelerators
    in High Performance Computing (SAAHPC'11), Knoxville, TN, July
    19-21, 2011.
  \item T.M. Evans, G.G. Davidson, and R.N. Slaybaugh,
    ''Three-Dimensional Full Core Power Calculations for Pressurized
    Water Reactors,'' Proceedings of the 2010 Scientific Discovery
    through Advanced Computing (SciDAC) Conference. Chattanooga,
    Tennessee, July 11-15, 2010. Oak Ridge National
    Laboratory. http://computing.ornl.gov/workshops/scidac2010/.
  \item G. Davidson and E.W. Larsen, ''Sweepless Time-Dependent
    Transport Calculations using the Staggered Block Jacobi Method,''
    International Conference on Mathematics, Computational Methods,
    and Reactor Physics (M\&C 2009), Saratoga Springs, NY, May 3-7.  On
    CD-ROM, American Nuclear Society, LaGrange Park, IL, 2009.
  \item G. Davidson and T.S. Palmer, ``Finite Element Transport Using
    Wachspress Rational Basis Functions on Quadrilaterals in Diffusive
    Regions,'' Palais des Papes, Avignon, France, September 12-15.  On
    CD-ROM, American Nuclear Society, LaGrange Park, IL, 2005.
\end{enumerate}

\leftsubheading{Conference Abstracts}
\begin{enumerate}
  \item S.P. Hamilton, G.G. Davidson, T.M. Evans, and K. Banerjee,
    "Accelerated Monte Carlo Fission Source Convergence with Fission
    Matrix and Kernel Density Estimators," American Nuclear Society
    Annual Summer Meeting, June 12-16, New Orleans, LA (2016).
  \item B. Vacaliuc, J.K. Munro, Jr., Z.W. Bell, T.M. Evans, and
    G.G. Davidson, "Accelerated Solution of One-Dimensional Neutron
    Transport on General Purpose Graphics Processing Unit,"
    International Conference on Preconditioning Techniques for
    Scientific and Industrial Applications," May 16-18, Bordeaux,
    France, 2011.
  \item G.G. Davidson, T.M. Evans, R.N. Slaybaugh, and C.G. Baker,
    "Massively Parallel Solutions to the k-Eigenvalue Problem,"
    Trans. Am. Nucl. Soc., 103 (2010).
  \item G. Davidson and E.W. Larsen, "An Unconditionally-Stable
    Time-Dependent Transport Method Without Sweeps,"
    Trans. Am. Nucl. Soc., 97 (2007).
  \item G. Davidson, J.D. Densmore, A.K. Prinja, and J.E. Morel,
    "Asymptotically Correct Angular Distributions for Monte
    Carlo-Diffusion Interfaces," Trans. Am. Nucl. Soc., 94 (2006).
  \item G.G. Davidson and T.S. Palmer, "Finite Element Diffusion on
    Arbitrary Quadrilaterals using Rational Basis Functions,"
    Trans. Am. Nucl. Soc., 87 (2002).
\end{enumerate}

\leftsubheading{Theses}
\begin{enumerate}
  \item G. Davidson, "Time-Dependent Radiation Transport Using the
    Staggered-Block Jacobi Method," Doctoral Dissertation, Department
    of Nuclear Engineering and Radiolocal Sciences, University of
    Michigan (2010).
  \item G. Davidson, "Finite Element Transport Using Wachspress
    Rational Basis Functions on Quadrilaterals in Diffusive Regions,"
    Master's Thesis, Department of Nuclear Engineering and Radiation
    Health Physics, Oregon State University (2004).
  \item G. Davidson, "Finite Element Diffusion Solutions on Arbitrary
    Quadrilaterals using Rational Basis Functions," Undergraduate
    Honor's Thesis, Department of Nuclear Engineering and Radiation
    Health Physics, Oregon State University (2002).
\end{enumerate}

\leftsubheading{Contributed Presentations}
\begin{enumerate}
  \item G.G. Davidson, T.M. Evans, R.N. Slaybaugh, and C.G. Baker,
    "Massively Parallel Solutions to the k-Eigenvalue Problem,"
    American Nuclear Society, Annual Meeting, November 7-11, 2010, Las
    Vegas, N.V.
  \item G. Davidson and E.W. Larsen, "An Unconditionally-Stable
    Finite-Element Transport Method Without Sweeps," American Nuclear
    Society, Annual Meeting, November 11-15, 2007, Washington, D.C.
  \item G. Davidson and T.S. Palmer, "Finite-Element Particle
    Transport using Wachspress Rational Basis Functions,"
    Computational Science Graduate Fellowship, Annual Conference, June
    20-22, 2006, Washington, D.C., available at
    http://www.cs-pi.org/csgf/conf/2006/presentations/davidson.shtml.
  \item G. Davidson, J.D. Densmore, A.K. Prinja, and J.E. Morel,
    "Asymptotically Correct Angular Distributions for Monte
    Carlo-Diffusion Interfaces," American Nuclear Socity, Annual
    Meeting, June 4-8, 2006, Reno, NV.
  \item G. Davidson and T.S. Palmer, "Finite Element Transport Using
    Wachspress Rational Basis Functions on Quadrilaterals in Diffusive
    Regions," Palais des Papes, Avignon, France, September 12-15,
    2005.
  \item G.G. Davidson and T.S. Palmer, "Finite Element Diffusion on
    Arbitrary Quadrilaterals using Rational Basis Functions," American
    Nuclear Society, Annual Meeting, November 17-21, 2002, Washington,
    D.C.
\end{enumerate}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Activities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Member of the American Nuclear Society, 1998-Present
  \begin{itemize}
    \item Local American Nuclear Society Executive Committee 2016 - Present
    \item Mathematics and Computations Division Executive Committee, 2011-2014
    \item Co-chair of the Mathematics and Computations Division
      Publicity Committee. 
	\item Vice President of the Student Chapter at Oregon State
      University, 1999-2000.
  \end{itemize}
\item Attended the 2011 MeV Summer School: Reactor Physics,
  Computations, Validation, and Integration in Multiphysics Codes 
\item Attended the 2008 Accerators for Science and Engineering
  Applications: GPUs and Multicores summer school 
\item Member of the American Nuclear Society, 1998-Present
\item Graduate Senator of the Associated Students of Oregon State
  University, 2004-2006.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Programming Languages: C++, C , Python, Fortran 90
\item Code Libraries: C++ Standard Template Libraries, BOOST,
  Trilinos, Silo, HDF5 
\item Version Control Software: CVS, Subversion, Git, Mercurial
\item Documentation: LaTex, Doxygen, reStructuredText, Wiki markup
\item Analysis Software: Mathematica, Matlab, Maple
\item Scientific Software: AMP, MCNP, Scale, Attila, VESTA, Serpent
\item Office Software: MS Office, OpenOffice
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
