% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author)
% http://mboedick.org (c) 2003-2007 David J. Grant
% <davidgrant-at-gmail.com> http://www.davidgrant.ca (c) 2008-2015
% Nathaniel Johnston <nathaniel@njohnston.ca> http://www.njohnston.ca
% This work is licensed under the Creative Commons
% Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of
% this license, visit
% http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter
% to Creative Commons, 543 Howard Street, 5th Floor, San Francisco,
% California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{hyperref}

% The following two lines are needed to fix a MacTex compatibility issue
% Thanks to Tony Blake for finding this fix!
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
% Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
% Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolor}{gray}{0.75}  
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars
\urlstyle{rm}

%-----------------------------------------------------------
% Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
      \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
	\textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}}
\newcommand{\olressubheading}[2]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
  \end{tabular*}}%\vspace{6pt}}
\newcommand{\leftsubheading}[1]{
  \textbf{#1}\vspace{-6pt} \\}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Gregory Davidson} & \textbf{\today} \\
  Senior Research and Development Staff &
  (865) 574-3921 \\
  Reactor and Nuclear Systems Division &
  \href{mailto:davidsongg@ornl.gov}{davidsongg@ornl.gov} \\
  Oak Ridge National Laboratory &
  \url{https://www.ornl.gov/staff-profile/gregory-g-davidson} \\  
  1 Bethel Valley Rd. & \\
  Oak Ridge, TN  37831 & \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

My research interests including computational physics algorithms for
high performance modeling and simulations applied to nuclear
applications, including deterministic neutral particle transport algorithms, such as finite element $S_N$ discretizations
      and time differencing methods, Monte Carlo transport,
      sensitivity/uncertainty analysis, multiphysics methods, transport-depletion coupling
      methods, high-performance simulations applied to problems in enrichment
      science, hydrodynamics, software engineering, object-oriented
      programming, programming for massively-parallel systems,
      especially leadership-class computing, and programming for
      heterogeneous architectures, including GPUs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \ressubheading{University of Michigan}{Ann Arbor,
    MI}{Ph.D. Nuclear Engineering and Radiological Sciences and
    Scientific Computing}{2004 - 2009}
  \vspace*{0.5\baselineskip}
  
	Time-Dependent Radiation Transport using
    the Staggered-Block Jacobi Method
    \vspace*{\baselineskip}
      
  \ressubheading{Oregon State University}{Corvallis, OR}{M.S. Nuclear
    Engineering}{2002 - 2004}
  \vspace*{0.5\baselineskip}
  
	  Finite Element Transport using Wachspress
        Rational Basis Functions on Quadrilaterals in Diffusive
        Regions
        \vspace*{\baselineskip}

  \ressubheading{Oregon State University}{Corvallis, OR}{Honor's
    B.S. Nuclear Engineering}{1998 - 2002}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \olressubheading{Oak Ridge National Laboratory}{2009 - Present}\\
  \textit{Senior research and development staff member}

  Current research efforts include research and development of
  high-performance Monte
  Carlo and hybrid deterministic radiation transport methods within
  the Exnihilo radiation transport suite, and integrated modeling task lead within the
  Advanced Simulation Initiatives in Nonproliferation Applications
  program, as well as ORNL team lead for the simulation of critical
  used nuclear fuel canisters within geological repositories.
  Previous research efforts include working on the VERA development team for
  the Consortium for the Advanced Simulation of Light Water Reactors
  (CASL), and as a developer for the SCALE code suite.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Significant Honors and Awards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item R\&D100 Award for the Virtual Environment for Reactor
  Applications (VERA) reactor simulator code.
\item 2014 ORNL Engineering Research and Development team award
\item HPC Innovation Excellence Award
\item 2010 ORNL Engineering Research and Development team award
\item D.O.E. Computational Science Graduate Fellowship Award
\end{itemize}  


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Significant Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{enumerate}
  \item Evan S. Gonzalez and Gregory G. Davidson, ``Choosing Transport
    Events for Initiating Splitting and Rouletting,'' Journal of
    Nuclear Engineering, \textbf{2}, 97--104 (2021),
    https://doi.org/10.3390/jne2020010.
  \item Cole Gentry, Benjamin Collins, Eva Davidson, Gregory Davidson,
    Thomas Evans, Andrew Godfrey, Shane Hart, Gemina Ilas, Seth
    Johnson, Kang Seog Kim, Scott Palmtag, Tara Pandya, Katherine
    Royston, William Wieselquist, and Gary Wolfram, ``Secondary Source
    Core Reload Modeling with VERA,'' Nucl. Sci. Eng., (2020)
    https://doi.org/10.1080/00295639.2020.1820797.
  \item Cihangir Celik, Douglas E. Peplow, Gregory G. Davidson, and
    Mathew R. Swinney, ``A Directional Detector Response Function for
    Anisotropic Detectors,'' Nucl. Sci. Eng., \textbf{193}(12),
    1355-1370 (2019) https://doi.org/10.1080/00295639.2019.1631028.
  \item Elliott D. Biondo, Thomas M. Evans, Gregory G. Davidson, and
    Steven P. Hamilton, ``Singular Value Decomposition of Adjoint Flux
    Distributions for Monte Carlo Variance Reduction,''
    Ann. Nucl. Energy, \textbf{141} (2020)
    https://doi.org/10.1080/00295450.2019.1625663. 
  \item Gregory G. Davidson, Tara M. Pandya, Seth R. Johnson, Thomas
    M. Evans, Aarno E. Isotalo, Cole A Gentry, and William
    A. Wieselquist, ``Nuclide Depletion Capabilities in the Shift Monte
    Carlo Code,'' Ann. Nucl. Energy, \textbf{114}, 259-276 (2018)
    https://doi.org/10.1016/j.anucene.2017.11.042.
  \item Elliott D. Biondo, Gregory G. Davidson, Tara M. Pandya,
    Steven P. Hamilton, and Thomas M. Evans, ``Deterministically
    Estimated Fission Source Distributions for Monte Carlo
    k-Eigenvalue Problems,'' Ann. Nucl. Energy, \textbf{119}, 7--22
    (2018) https://doi.org/10.1016/j.anucene.2018.04.039.
  \item Lei Jin, Kaushik Banerjee, Steven P. Hamilton, and Gregory
    G. Davidson, ``Improving Variance Estimation in Monte Carlo
    Eigenvalue Simulations,'' Ann. Nucl. Energy, \textbf{110}, 692-708
    (2017). 
  \item Aarno E. Isotalo, Gregory G. Davidson, Tara M. Pandya, William
    A. Wieselquist, and Seth R. Johnson, ``Flux Renormalization in
    Constant Power Burnup Calculations,'' Ann. Nucl. Energy,
    \textbf{96}, 148-157 (2016)
    https://doi.org/10.1016/j.anucene.2017.07.016.
  \item Steven P. Hamilton, Thomas M. Evans, Gregory G. Davidson, Seth
    R. Johnson, Tara M. Pandya, and Andrew T. Godfrey, ``Hot Zero
    Power Reactor Calculations Using the Insilico Code,''
    J. Comp. Phys., \textbf{314}, 700-711 (2016)
    https://doi.org/10.1016/j.jcp.2016.03.033.
  \item Tara M. Pandya, Seth R. Johnson, Thomas M. Evans, Gregory
    G. Davidson, Steven P. Hamilton, and Andrew T. Godfrey,
    ``Implementation, Capabilities, and Benchmarking of Shift, a
    Massively Parallel Monte Carlo Radiation Transport Code,''
    J. Comp. Phys., \textbf{308}, 239-272 (2016)
    https://doi.org/10.1016/j.jcp.2015.12.037.
  \item Gregory G. Davidson, Thomas M. Evans, Joshua J. Jarrell,
    Steven P. Hamilton, Tara M. Pandya, and Rachel N. Slaybaugh, ``Massively
    Parallel, Three-Dimensional Transport Solutions for the
    k-Eigenvalue Problem,'' Nucl. Sci. Eng. \textbf{177}, 111-125
    (2014) https://doi.org/10.13182/NSE12-101.
\item G. Davidson and E.W. Larsen, ``Sweepless Time-Dependent
    Transport Calculations using the Staggered Block Jacobi Method,''
    International Conference on Mathematics, Computational Methods,
    and Reactor Physics (M\&C 2009), Saratoga Springs, NY, May 3-7.  On
    CD-ROM, American Nuclear Society, LaGrange Park, IL, 2009.
  \item Gregory G. Davidson and Todd S. Palmer, ``Finite Element
    Transport Using Wachspress Rational Functions on Quadrilaterals in
    Thick Diffusive Regions,'' Nucl. Sci. Eng., \textbf{159}(242)
    (2008) https://doi.org/10.13182/NSE159-242.
  \item Jeffrey D. Densmore, Gregory G. Davidson, and David
    B. Carrington, ``Emmissivity of Discretized Diffusion Problems,''
    Ann. Nucl. Energy, \textbf{33}, (2006)
    https://doi.org/10.1016/j.anucene.2006.02.006.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
