% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author)
% http://mboedick.org (c) 2003-2007 David J. Grant
% <davidgrant-at-gmail.com> http://www.davidgrant.ca (c) 2008-2015
% Nathaniel Johnston <nathaniel@njohnston.ca> http://www.njohnston.ca
% This work is licensed under the Creative Commons
% Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of
% this license, visit
% http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter
% to Creative Commons, 543 Howard Street, 5th Floor, San Francisco,
% California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{hyperref}

% The following two lines are needed to fix a MacTex compatibility issue
% Thanks to Tony Blake for finding this fix!
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
% Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
% Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolor}{gray}{0.75}  
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars
\urlstyle{rm}

%-----------------------------------------------------------
% Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
      \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
	\textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}}
\newcommand{\olressubheading}[2]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
  \end{tabular*}}%\vspace{6pt}}
\newcommand{\leftsubheading}[1]{
  \textbf{#1\vspace{-6pt} \\}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Gregory Davidson} & \textbf{\today} \\
  Senior Research and Development Staff &
  (865) 574-3921 \\
  Reactor and Nuclear Systems Division &
  \href{mailto:davidsongg@ornl.gov}{davidsongg@ornl.gov} \\
  Oak Ridge National Laboratory &
  \url{https://www.ornl.gov/staff-profile/gregory-g-davidson} \\  
  1 Bethel Valley Rd. & \\
  Oak Ridge, TN  37831 & \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{center}
    \parbox{6.762in}{My research interests include deterministic
      transport algorithms, such as finite element SN discretizations
      and time differencing methods, Monte Carlo transport,
      sensitivity/uncertainty analysis, discrete diffusion Monte Carlo
      methods, multiphysics methods, transport-depletion coupling
      methods, hydrodynamics, software engineering, object-oriented
      programming, programming for massively-parallel systems,
      especially leadership-class computing, and programming for
      heterogeneous architectures, including GPUs.}
  \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
  \ressubheading{University of Michigan}{Ann Arbor,
    MI}{Ph.D. Nuclear Engineering and Radiological Sciences and
    Scientific Computing}{2004 - 2009}
  \begin{itemize}
	\resitem{Dissertation: Time-Dependent Radiation Transport
      using the Staggered-Block Jacobi Method}
	\resitem{GPA: 8.15/9.00}
  \end{itemize}

\item
  \ressubheading{Oregon State University}{Corvallis, OR}{M.S. Nuclear
    Engineering}{2002 - 2004}
	\begin{itemize}
	  \resitem{Thesis: Finite Element Transport using Wachspress
        Rational Basis Functions on Quadrilaterals in Diffusive Regions}
		\resitem{GPA: 3.93 / 4.00}
	\end{itemize}

\item
  \ressubheading{Oregon State University}{Corvallis, OR}{Honor's
    B.S. Nuclear Engineering}{1998 - 2002}
	\begin{itemize}
	  \resitem{Undergraduate Thesis: Finite Element Diffusion
        Solutions on Arbitrary Quadrilaterals using Wachspress
        Rational Functions}
		\resitem{GPA: 3.94 / 4.00}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
  \olressubheading{Oak Ridge National Laboratory}{2009 - Present}
  Research and development associate as part of the Shift/Denovo team,
  investigating advanced, massively parallel radiation transport
  solutions, including both fixed-source and k-eigenvalue problems, as
  well as transport-depletion coupling schemes.  Also part of the
  development team of CASL as a member of the VERA-RTM area.  Have
  worked extensively in multicode coupling, including coupling to the
  XSProc package in Scale for automated cross-section generation,
  coupling to ORIGEN for depletion calculations, and to the AMP
  (Advanced MultiPhysics) fuel performance code.

\item
  \olressubheading{Los Alamos National Laboratory}{Summer 2005}
  Implemented an emissivity-preserving discrete diffusion Monte Carlo
  (DDMC) transport scheme in C++.  Wrote and tested the
  asymptotically-correct angular distribution functionality for
  transport-diffusion interfaces in DDMC methods.

\item
  \olressubheading{Bettis Atomic Power Laboratory}{Summer 2003}
  Derived the equations for the constant-constant, constant-linear,
  and linear-linear short characteristics methods on rectangular
  zones.  Wrote the constant-linear characteristics method into an
  existing SN code in Fortran 90.

\item
  \olressubheading{Lawrence Livermore National Laboratory}{Summer
    2002}
  Researched a finite-element transport method using Wachspress
  rational basis functions for solving the  discrete-ordinates neutron
  transport equation. 

\item
  \olressubheading{Lawrence Livermore National Laboratory}{Summer
    2001}
  Investigated a one-dimensional computational hydrodynamics scheme
  based on rational basis functions.

\item
  \olressubheading{Lawrence Livermore National Laboratory}{Summer
    2000}
  Implemented relativistic fluid motion corrections and momentum
  deposition into the particle Monte Carlo package of Kull, a
  three-dimensional multiphysics code, in C++ and Python. 
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Honors and Awards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item R\&D100 Award for the Virtual Environment for Reactor
  Applications (VERA) reactor simulator code.
\item 2014 ORNL Engineering Research and Development team award
\item Principle Investigator of the ORNL LDRD, "Advanced Modeling \&
  Simulation to Support High Performance Research Reactor Conversions
  to Low Enriched Uranium"
\item Principle Investigator of the ASCR Leadership Computing
  Challenge, "Advanced Simulation of HFIR for LEU Conversion"
\item Awarded the HPC Innovation Excellence Award
\item 2012 Oak Ridge National Laboratory Significant Event Award
\item 2011 MeV Summer School: Best Technical Paper Award
\item American Nuclear Society, Mathematics and Computation
  Division, Best Paper and Presentation Award, November 2010
\item 2010 ORNL Engineering Research and Development team award
\item D.O.E. Computational Science Graduate Fellowship Award
\item Master's Thesis of the Year, Nuclear Engineering
  Department, Oregon State University
\item Honor's College Member at Oregon State University
\item Tau Beta Pi Engineering Honor Society
\item Phi Kappa Phi Honor Society
\item Alpha Lambda Delta Honorary Fraternity
\item National Academy for Nuclear Training Scholarship
\item Oregon Space Grant Scholarship
\item D.O.E. NEHP Scholarship
\item OSU Achievement Scholarship
\item Schuette Engineering Scholarship
\item Leo Adler Foundation Scholarship
\item Sanford Adler Scholarship
\item Nadie Strayer Scholarship
\item Grant-Baker Federal Credit Union Scholarship
\item Elks Scholarship
\end{itemize}  


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Journal Publications}
\begin{enumerate}
  \item Cole Gentry, Benjamin Collins, Eva Davidson, Gregory Davidson,
    Thomas Evans, Andrew Godfrey, Shane Hart, Gemina Ilas, Seth
    Johnson, Kang Seog Kim, Scott Palmtag, Tara Pandya, Katherine
    Royston, William Wieselquist, and Gary Wolfram, ``Secondary Source
    Core Reload Modeling with VERA,'' Nucl. Sci. Eng. (to appear).
  \item Cihangir Celik, Douglas E. Peplow, Gregory G. Davidson, and
    Mathew R. Swinney, ``A Directional Detector Response Function for
    Anisotropic Detectors,'' Nucl. Sci. Eng., \textbf{193}(12),
    1355-1370 (2019) https://doi.org/10.1080/00295639.2019.1631028.
  \item Douglas E. Peplow, Kaushik Banerjee, Gregory G. Davidson, Ian
    R. Stewart, Mathew W. Swinney, and Jackson N. Wagner, ``Preliminary
    Validation of the Shift Monte Carlo Code for Fixed-Source
    Radiation Transport Problems,'' Nucl. Tech., \textbf{206}(1),
    107--125 (2020) https://doi.org/10.1080/00295450.2019.1625663.
  \item Elliott D. Biondo, Thomas M. Evans, Gregory G. Davidson, and
    Steven P. Hamilton, ``Singular Value Decomposition of Adjoint Flux
    Distributions for Monte Carlo Variance Reduction,''
    Ann. Nucl. Energy, \textbf{141} (2020)
    https://doi.org/10.1080/00295450.2019.1625663. 
  \item Gregory G. Davidson, Tara M. Pandya, Seth R. Johnson, Thomas
    M. Evans, Aarno E. Isotalo, Cole A Gentry, and William
    A. Wieselquist, ``Nuclide Depletion Capabilities in the Shift Monte
    Carlo Code,'' Ann. Nucl. Energy, \textbf{114}, 259-276 (2018)
    https://doi.org/10.1016/j.anucene.2017.11.042.
  \item Elliott D. Biondo, Gregory G. Davidson, Tara M. Pandya,
    Steven P. Hamilton, and Thomas M. Evans, ``Deterministically
    Estimated Fission Source Distributions for Monte Carlo
    k-Eigenvalue Problems,'' Ann. Nucl. Energy, \textbf{119}, 7--22
    (2018) https://doi.org/10.1016/j.anucene.2018.04.039.
  \item Lei Jin, Kaushik Banerjee, Steven P. Hamilton, and Gregory
    G. Davidson, ``Improving Variance Estimation in Monte Carlo
    Eigenvalue Simulations,'' Ann. Nucl. Energy, \textbf{110}, 692-708
    (2017). 
  \item Aarno E. Isotalo, Gregory G. Davidson, Tara M. Pandya, William
    A. Wieselquist, and Seth R. Johnson, ``Flux Renormalization in
    Constant Power Burnup Calculations,'' Ann. Nucl. Energy,
    \textbf{96}, 148-157 (2016)
    https://doi.org/10.1016/j.anucene.2017.07.016.
  \item Steven P. Hamilton, Thomas M. Evans, Gregory G. Davidson, Seth
    R. Johnson, Tara M. Pandya, and Andrew T. Godfrey, ``Hot Zero
    Power Reactor Calculations Using the Insilico Code,''
    J. Comp. Phys., \textbf{314}, 700-711 (2016)
    https://doi.org/10.1016/j.jcp.2016.03.033.
  \item Tara M. Pandya, Seth R. Johnson, Thomas M. Evans, Gregory
    G. Davidson, Steven P. Hamilton, and Andrew T. Godfrey,
    ``Implementation, Capabilities, and Benchmarking of Shift, a
    Massively Parallel Monte Carlo Radiation Transport Code,''
    J. Comp. Phys., \textbf{308}, 239-272 (2016)
    https://doi.org/10.1016/j.jcp.2015.12.037.
  \item Rachel N. Slaybaugh, Thomas M. Evans, Gregory G. Davidson, and
    Paul P.H. Wilson, ``Multigrid in Energy Preconditioner for Krylov
    Solvers,'' J. Comp. Phys., \textbf{272}, 405-419 (2013)
    https://doi.org/10.1016/j.jcp.2013.02.012.
  \item Gregory G. Davidson, Thomas M. Evans, Joshua J. Jarrell,
    Steven P. Hamilton, Tara M. Pandya, and Rachel N. Slaybaugh, ``Massively
    Parallel, Three-Dimensional Transport Solutions for the
    k-Eigenvalue Problem,'' Nucl. Sci. Eng. \textbf{177}, 111-125
    (2014) https://doi.org/10.13182/NSE12-101.
  \item Joshua J. Jarrell, Andrew T. Godfrey, Thomas M. Evans, and
    Gregory G. Davidson, ``Full Core Reactor Analysis: Running Denovo
    on Jaguar,'' Nucl. Sci. Eng., \textbf{175}, 283-291 (2013)
    https://doi.org/10.13182/NSE12-60.
  \item Gokhan Yesilyurt, Kevin T. Clarno, Thomas M. Evans, Gregory
    G. Davidson, and P.B. Fox, ``A C5 Benchmark Problem with Discrete
    Ordinate Radiation Transport Code Denovo,''
    Nucl. Tech. \textbf{176}(2), 274-283 (2011)
    https://doi.org/10.13182/NT11-A13301.
  \item Gregory G. Davidson and Todd S. Palmer, ``Finite Element
    Transport Using Wachspress Rational Functions on Quadrilaterals in
    Thick Diffusive Regions,'' Nucl. Sci. Eng., \textbf{159}(242)
    (2008) https://doi.org/10.13182/NSE159-242.
  \item Jeffrey D. Densmore, Gregory G. Davidson, and David
    B. Carrington, ``Emmissivity of Discretized Diffusion Problems,''
    Ann. Nucl. Energy, \textbf{33}, (2006)
    https://doi.org/10.1016/j.anucene.2006.02.006.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Conference Proceedings}
\begin{enumerate}
  \item Benjamin R. Betzler, David Chandler, Thomas M. Evans, Gregory
    G. Davidson, Charles R. Daily, Stephen C. Wilson, Scott W. Mosher,
    ``As-Built Simulation of the High Flux Isotope Reactor,'' PHYSOR
    2020, Mar. 29 - April 2 (2020).
  \item Gregory G. Davidson, Seth R. Johnson, Stylianos Chatzidakis,
    Abiodun Adeniyi, and Kaushik Banerjee, ``Development of Terrenus,
    a Multiphysics Code for Spent Nuclear Fuel Cask Criticality
    Analysis,'' 11th International Conference on Nuclear Criticality
    Safety, Paris, Sept. 15 - 20 (2019).
  \item Cole Gentry, Andrew Godfrey, Tara Pandya, Gregory Davidson, and
    F. Franceschini, ``AP1000 Benchmarking of VERA Neutronics
    Toolset,'' M\&C 2017 – International Conference on Mathematics and
    Computational Methods Applied to Nuclear Science and Engineering,
    Jeju, Korea, April 16-20 (2017).
  \item G.G. Davidson, T.M. Pandya, A.E. Isotalo, S.R. Johnson,
    T.M. Evans, and W.A. Wieselquist, ``Nuclide Depletion Capabilities
    in the Shift Monte Carlo Code,'' PHYSOR 2016, May 1-5, Sun Valley,
    ID.
  \item T.M. Pandya, S.R. Johnson, G.G. Davidson, T.M. Evans, and
    S.P. Hamilton, ``Shift: A Massively Parallel Monte Carlo Radiation
    Transport Package,'' M\&C 2015, April 19-23, Nashville, TN.
  \item T.M. Evans, W. Joubert, S.P. Hamilton, S.R. Johnson,
    J.A. Turner, G.G. Davidson, and T.M. Pandya, ``Three-Dimensional
    Discrete Ordinates Reactor Assembly Calculations on GPUs,'' M\&C
    2015, April 19-23, Nashville, TN.
  \item R.N. Slaybaugh, T.M. Evans, G.G. Davidson, and P.P.H. Wilson,
    ``Rayleigh Quotient Iteration with a Multigrid in Energy
    Preconditioner for Massively Parallel Neutron Transport,'' M\&C
    2015, April 19-23, Nashville, TN.
  \item Thomas M. Evans, Wayne Joubert, Steven P. Hamilton, Seth
    R. Johnson, John A. Turner, Gregory G. Davidson, and Tara
    M. Pandya, ``Three-Dimensional Discrete Ordinates Reactor
    Assembly Calculations on GPUs,'' ANS M\&C2015, Nashville, TN,
    April 19-23, (2015).
  \item S. Palmtag, K. Clarno, G. Davidson, et. al., ``Coupled
    Neutronics and Thermal-Hydraulic Solution of a Full-Core PWR Using
    VERA-CS,'' PHYSOR 2014, Kyoto, Japan.
  \item J.J. Jarrell, T.M. Evans, and G.G. Davidson, ``Discrete
    Ordinate Quadrature Selection for Reactor-based Eigenvalue
    Problems,'' M\&C 2013, Sun Valley, ID May 5-9, 2013.
  \item S. Hamilton, K. Clarno, M. Berrill, T. Evans, G. Davidson,
    R. Lefebvre, and R. Sampath, ``Multiphysics Simulations for LWR
    Analysis,'' M\&C 2013, Sun Valley, ID, May 5-9, 2013.
  \item C.G. Baker, G.G. Davidson, T.M. Evans, S.P. Hamilton,
    J.J. Jarrell, and W. Joubert, ``High Performance Radiation
    Transport Simulations on Titan,'' Supercomputing SC12, Salt Lake
    City, NV, Nov. 12-15, 2012.
  \item J.J. Jarrell, A.T. Godfrey, T.M. Evans, and G.G. Davidson,
    ``Full Core Reactor Analysis: Running Denovo on Jaguar,'' PHYSOR
    2012, Knoxville, TN, April 15-20. On CD-ROM, American Nuclear
    Society, LaGrange Park, IL, 2012.
  \item R.N. Slaybaugh, T.M. Evans, G.G. Davidson, and P.P.H. Wilson,
    ``Rayleigh Quotient Iteration in 3D, Deterministic Neutron
    Transport,'' PHYSOR 2012, Knoxville TN, April 15-20.  On CD-ROM,
    American Nuclear Society, LaGrange, Park, IL, 2012.
  \item B. Vacaliuc, D.R. Patlolla, E. D'Avezado, G.G. Davidson,
    et. al., ``Python for Development of OpenMP and CUDA Kernals for
    Multidimensional Data,'' 2011 Symposium on Application Accelerators
    in High Performance Computing (SAAHPC'11), Knoxville, TN, July
    19-21, 2011.
  \item T.M. Evans, G.G. Davidson, and R.N. Slaybaugh,
    ``Three-Dimensional Full Core Power Calculations for Pressurized
    Water Reactors,'' Proceedings of the 2010 Scientific Discovery
    through Advanced Computing (SciDAC) Conference. Chattanooga,
    Tennessee, July 11-15, 2010. Oak Ridge National
    Laboratory. http://computing.ornl.gov/workshops/scidac2010/.
  \item G. Davidson and E.W. Larsen, ``Sweepless Time-Dependent
    Transport Calculations using the Staggered Block Jacobi Method,''
    International Conference on Mathematics, Computational Methods,
    and Reactor Physics (M\&C 2009), Saratoga Springs, NY, May 3-7.  On
    CD-ROM, American Nuclear Society, LaGrange Park, IL, 2009.
  \item G. Davidson and T.S. Palmer, ``Finite Element Transport Using
    Wachspress Rational Basis Functions on Quadrilaterals in Diffusive
    Regions,'' M\&C 2005, Palais des Papes, Avignon, France, September
    12-15.  On CD-ROM, American Nuclear Society, LaGrange Park, IL,
    2005.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Conference Summaries}
\begin{enumerate}
  \item Gregory G. Davidson, Seth R. Johnson, and Stylianos
    Chatzidaki, ``Development of Terrenus: A Multiphysics Code for
    Spent Nuclear Fuel Canister Criticality Analysis,'' Transactions
    of the American Nuclear Society, v. 121, Washington
    D.C. Nov. 17-21 (2019).
  \item Andrew D. Nicholson, Daniel E. Archer, Mark S. Bandstra,
    Gregory G. Davidson, Irakli Garishvili, Douglas E. Peplow,
    M.S. Lance McLean, William R. Ray, Ian R. Stewart, Mathew
    W. Swinney, Michael J. Willis, Brian J. Quiter, ``Virtual Test
    Beds for Radiation Detector and Algorithm Development,''
    International Conference on Methods and Applications of
    Radioanalytical Chemistry (MARC XI), April 8 - 13, Kailua-Kona,
    HI (2018).
  \item Peplow, D.E., Swinney, Mathew W., Davidson, Gregory G.,
    Nicholson, Andrew D., and Patton, Bruce W., ``Initial Modeling of
    Urban Search Measurements,'' American Nuclear Society Annual
    Meeting, June 11 – 15, Chicago, IL (2017).
  \item A.D. Nicholson, I. Garishvili, D.E. Peplow, D.E. Archer,
    W.R. Ray, M.W. Swinney, M.J. Willis, G.G. Davidson,
    S.L. Cleveland, B.W. Patton, D.E. Hornback, J.J. Peltz,
    M.S.L. McLean, A.A. Plionis, B.J. Quiter, and M.S. Bandstra,
    ``Multiagency Urban Seach Experiment Detector and Algorithm Test
    Bed,'' IEEE Trans. Nucl. Sci., 64, 7, 1689-1695 (2017)
    https://doi.org/10.1109/TNS.2017.2677092.
  \item Lei Jin, Kaushik Banerjee, Steven P. Hamilton, and Gregory
    G. Davidson, ``Variance Estimation in Monte Carlo Eigenvalue
    Simulations Using Spectral Analysis Method,'' Transactions of
    the American Nuclear Society, (2017).
  \item Douglas E. Peplow, Mathew W. Swinney, Gregory G. Davidson,
    Andrew D. Nicholson, and Bruce W. Patton, ``Initial Modeling of
    Urban Search Measurements,'' Transactions of the American Nuclear
    Society, \textbf{116}, 913--916 (2017).
    https://www.osti.gov/biblio/1362237.
  \item Gregory G. Davidson and Kaushik Banerjee, ``Towards On-the-Fly
    Dose Analysis Using the Shift Monte Carlo Code,'' Transactions of
    the American Nuclear Society, \textbf{117}, 1178--1181 (2017).
  \item S.P. Hamilton, G.G. Davidson, T.M. Evans, and K. Banerjee,
    ``Accelerated Monte Carlo Fission Source Convergence with Fission
    Matrix and Kernel Density Estimators,'' American Nuclear Society
    Annual Summer Meeting, June 12-16, New Orleans, LA (2016).
  \item Irakli Garishvili, Donald Hornback, Dan Archer, Andrew
    Nicholson, Douglas Peplow, Greg Davidson, Mathew Swinney, Jim
    Peltz, Lance McLean, Brian Quiter, ``MUSE - Multi-agency Urban
    Search Experiments,'' SORMA West, May (2016).
  \item B. Vacaliuc, J.K. Munro, Jr., Z.W. Bell, T.M. Evans, and
    G.G. Davidson, ``Accelerated Solution of One-Dimensional Neutron
    Transport on General Purpose Graphics Processing Unit,''
    International Conference on Preconditioning Techniques for
    Scientific and Industrial Applications," May 16-18, Bordeaux,
    France, 2011.
  \item G.G. Davidson, T.M. Evans, R.N. Slaybaugh, and C.G. Baker,
    ``Massively Parallel Solutions to the k-Eigenvalue Problem,''
    Trans. Am. Nucl. Soc., 103 (2010).
  \item G. Davidson and E.W. Larsen, ``An Unconditionally-Stable
    Time-Dependent Transport Method Without Sweeps,''
    Trans. Am. Nucl. Soc., 97 (2007).
  \item G. Davidson, J.D. Densmore, A.K. Prinja, and J.E. Morel,
    ``Asymptotically Correct Angular Distributions for Monte
    Carlo-Diffusion Interfaces,'' Trans. Am. Nucl. Soc., 94 (2006).
  \item G.G. Davidson and T.S. Palmer, ``Finite Element Diffusion on
    Arbitrary Quadrilaterals using Rational Basis Functions,''
    Trans. Am. Nucl. Soc., 87 (2002).
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Reports}
\begin{enumerate}
  \item Gregory G. Davidson, Santosh Bhatt, Mathew W. Swinney, Elliott
    D. Biondo, Jose Salcedo-Perez, Kaushik Banerjee, Alex Perry, Ethan
    Asano, Evan S. Gonzalez, and Brian C. Kiedrowski, ``Initial
    Coupled Simulations of a Critical Dual-Purpose Canister in a
    Saturated Repository,'' M3SF-20OR010305016, ORNL/SPR-2020/XXXX (to
    appear).
  \item L.L. Price, A.A. Alsaed, P.V. Brady, F. Gelbard, V. Mousseau,
    M. Nole, J.L. Prouty, A. Salazar, K. Banerjee, S. Bhatt,
    G.G. Davidson, S.L. Painter, M. Swinney, E. Gonzalez, ``Status
    Report -- Progress in Developing a Repository-Scale Performance
    Assessment Model,'' M4SF-20SN010305064 (to appear).
  \item Seth R. Johnson, Thomas M. Evans, Gregory G. Davidson, Steven
    P. Hamilton, Tara M. Pandya, Katherine E. Royston, and Elliott
    D. Biondo, ``Omnibus User Manual'', ORNL/TM-2018/1073 (2020).
  \item Kaushik Banerjee, Cihangir Celik, Gregory G. Davidson,
    Thomas M. Evans, Bradley T. Rearden, William A. Wieselquist,
    ``The MAVRIC-Shift Sequence in SCALE for Radiation Transport and
    Shielding Calculations with Automated Variance Reduction and
    Parallel Computing,'' ORNL/TM-2019/1358 (2020).
  \item Gregory G. Davidson, Mathew Swinney, Seth Johnson, Santosh
    Bhatt, and Kaushik Banerjee, ``Initial Neutronics and
    Thermal-Hydraulic Coupling for Spent Nuclear Fuel Canister,''
    M3SF-19OR010305015, ORNL/SPR-2019/1333 (2019).
  \item B.R. Betzler, E.E. Davidson, G.G. Davidson, T.M. Evans,
    S.C. Wilson, S.W. Mosher, G. Ilas, C.R. Daily, A.J. Conant,
    D. Chandler, ``Reactor Physics Modeling of the Cycle 483 Event
    in the High Flux Isotope Reactor,'' ORNL/TM-2018/1102 (2018).
  \item Daniel E. Archer, Mark S. Bandstra, David S. Bolme, Steven
    L. Cleveland, Joseph C. Curtis, Gregory G. Davidson, Irakli
    Garishvili, Jeffrey O. Johnson, Aravind K. Mikkilineni, M.S. Lance
    McLean, Andrew D. Nicholson, Douglas E. Peplow, Alexander
    A. Plionis, Matthew J. Poska, Brian J. Quiter, William R. Ray,
    Andrew J. Rowe, Ian R. Stewart, Mathew W. Swinney, and Michael
    J. Willis, ``Mid-Project Report for the Modeling Urban Scenarios and
    Experiments (MUSE) Project,'' ORNL/TM-2018/964, Oak Ridge National
    Laboratory, Oak Ridge, TN, (2018).
  \item Thomas M. Evans, Gregory G. Davidson, Steven P. Hamilton,
    and Kaushik Banerjee, ``Criticality Consequence Analysis Roadmap
    for a Spent Nuclear Fuel Canister in a Repository,'' Spent Fuel
    and Waste Disposition M3SF-18OR0103050111, ORNL/SPR-2018/951
    (2018). 
  \item Daniel E. Archer, Mark S. Bandstra, Gregory G. Davidson,
    Steven L. Cleveland, Irakli Garishvili, Donald E. Hornback,
    Jeffrey O. Johnson, M.S. Lance McLean, Andrew D. Nicholson, Bruce
    W. Patton, Douglas E. Peplow, Alexander A. Plionis, Brian
    J. Quiter, William R. Ray, Andrew J. Rowe, Mathew W. Swinney,
    Michael J. Willis, ``Modeling and Urban Search Experiments: Fort
    Indiantown Gap Data Collections Summary and Analysis,''
    ORNL/TM-2017/371, Oak Ridge National Laboratory, Oak Ridge, TN
    (2017) http://dx.doi.org/10.2172/1410932.
  \item Brian J. Ade, Kursat Bekar, Gregory Davidson, Elliott
    Biondo, ``Integration of the Shift Monte Carlo Framework into
    SCALE/TRITON and Addition of Few-Group Cross Section Tallies to
    Shift,'' ORNL/SPR-2017/523, Oct. (2017).
  \item Gregory G. Davidson and Kaushik Banerjee, ``Initial
    Development of a Large Facility Dose Analysis Approach,''
    SFWD-PO-2017-000084, ORNL/SPR-2017/439, Aug. 31 (2017).
  \item Elliott Biondo, Gregory Davidson, and Thomas Evans, ``Monte
    Carlo Fission Source Convergence Acceleration with
    Deterministically Estimated Fission Source Distributions,''
    ORNL/SR-2017/101, Oak Ridge National Laboratory, Oak Ridge, TN,
    (2017).
  \item Tara Pandya, Tom Evans, Greg Davidson, Seth Johnson, ``Shift
    Validation Plan for CASL,'' CASL-U-2016-1192-000,
    ORNL/TM-2016/538, Apr. (2016).
  \item Gregory Davidson and Kaushik Banerjee, ``Initial
    Implementation of On-the-Fly Dose Analysis,'' ORNL/TM-2016.463,
    Oak Ridge National Laboratory, Oak Ridge, TN (2016).
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Theses}
\begin{enumerate}
  \item G. Davidson, ``Time-Dependent Radiation Transport Using the
    Staggered-Block Jacobi Method,'' Doctoral Dissertation, Department
    of Nuclear Engineering and Radiolocal Sciences, University of
    Michigan (2010).
  \item G. Davidson, ``Finite Element Transport Using Wachspress
    Rational Basis Functions on Quadrilaterals in Diffusive Regions,''
    Master's Thesis, Department of Nuclear Engineering and Radiation
    Health Physics, Oregon State University (2004).
  \item G. Davidson, ``Finite Element Diffusion Solutions on Arbitrary
    Quadrilaterals using Rational Basis Functions,'' Undergraduate
    Honor's Thesis, Department of Nuclear Engineering and Radiation
    Health Physics, Oregon State University (2002).
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Contributed Presentations}
\begin{enumerate}
  \item Elliott Biondo, Gregory Davidson, Thomas Evans, Steven
    Hamilton, Seth Johnson, Tara Pandya, Katherine Royston, and Jose
    Salcedo-Perez, ``GPU-Accelerated Monte Carlo Radiation Transport
    with Shift,'' Roundtable, Current Issues in Computational Methods,
    American Nuclear Society Winter Meeting, Washington, DC, Nov. 18
    (2019).
  \item Gregory G. Davidson, Seth R. Johnson, Stylianos Chatzidakis,
    Abiodun Adeniyi, Kaushik Banerjee, Santosh Bhatt, ``Development
    of Terrenus, a Multiphysics Code for Spent Nuclear Fuel Cask
    Criticality Analysis,'' American Nuclear Society, Annual
    Meeting, Washington D.C., Nov. (2019).
  \item Cole Gentry, Andrew Godfrey, Eva Davidson, Germina Ilas,
    Benjamin Collins, Shane Hart, Kang Seog Kim, Tara Pandya,
    Katherine Royston, Gregory Davidson, Seth Johnson, Thomas Evans,
    Gary Wolfram, and Scott Palmtag, ``Source Range Detector
    Response Modeling using VERA'', Global and Top Fuel 2019,
    Seattle, Wa, Sept. (2019).
  \item Gregory Davidson, Alex Hackett, Douglas Peplow, and Will
    Ray, ``Using DagMC with Shift for Modeling Urban Scenarios and
    Experiments (MUSE),'' DagMC Workshop, Madison, Ws, Sept. (2019).
  \item Gregory G. Davidson, Seth R. Johnson, Stylianos Chatzidakis,
    Abiodun Adeniyi, Kaushik Banerjee, and Santosh Bhatt,
    ``Development of Terrenus, a Multiphysics Code for Spent Nuclear
    Fuel Cask Criticality Analysis,'' International Conference on
    Nuclear Criticality Safety (ICNC 2019), Paris, France,
    Sept. (2019).
  \item Gregory Davidson, Seth Johnson, Stylianos Chatzidakis, Kaushik
    Banerjee, ``Initial Neutronics and Thermal-Hydraulic Coupling for
    Spent Nuclear Fuel Canister,'' Spent Fuel and Waste Disposition
    Annual Working Group Meeting, UNLV-SEB, Las Vegas, NV, May 21-23
    (2019). 
  \item Kursat B. Bekar, Cihangir Celik, Gregory Davidson, Thomas
    Evans, Shane Hart, Brandon Langley, Robert Lefebvre, Seth
    Johnson, B.J. Marshall, Tara Pandya, and Ellen Saylor,
    ``CSAS/Shift Integration in SCALE 6.3,'' 2019 SCALE Users Group
    Workshop, Oak Ridge, TN. Aug. (2019).
  \item Matthew Jessee, Gregory G. Davidson, Andrew Holcomb, Shane
    Hart, and Will Wieselquist, ``Nodal Data Calculation in
    TRITON/Shift Part I: Applications,'' 2019 SCALE Users Group
    Workshop, Oak Ridge, TN. Aug. (2019).
  \item Will Wieselquist, Gregory G. Davidson, Andrew Holcomb, Shane
    Hart, and Matthew Jessee, ``Nodal Data Calculation in
    TRITON/Shift Part II: Method,'' 2019 SCALE Users Group Workshop,
    Oak Ridge, TN. Aug. (2019).
  \item B. Ade, K. Bekar, G. Davidson, T. Evans, S. Hart, M. Jessee,
    B. Langley, K. Royston, W. Wieselquist, ``Nodal Data
    Generation,'' 2018 SCALE Users Group Workshop, Oak Ridge, TN.,
    Aug. (2019).
  \item Elliott Biondo, Gregory Davidson, Thomas Evans, Steven
    Hamilton, Seth Johnson, Tara Pandya, Katherine Roystone,
    ``Exnihilo Radiation Transport Tutorial,'' RPSD 2018 Workshop,
    Santa Fe, NM, Aug. 26 (2018).
  \item Andrew Nicholson, Daniel E. Archer, Mark S. Bandstra,
    Gregory G. Davidson, Irakli Garishvili, Douglas E. Peplow,
    M.S. Lance McLean, Will R. Ray, Mathew W. Swinney, Michael
    J. Willis, and Brian J. Quiter, ``Virtual Testbeds for Radiation
    Detector and Algorithm Development,'' Methods and Applications
    of Radioanalytic AL Chemistry, Kailua Kona, HI, Apr. (2018).
  \item Gregory G. Davidson and Kaushik Banerjee, ``Toward
    On-the-Fly Dose Analysis using the Shift Monte Carlo Code,''
    American Nuclear Society, Annual Meeting, Washington, D.C.,
    Oct. 29 -- Nov. 2 (2017).
  \item Gregory Davidosn, Elliott Biondo, Thomas Evans, Seth
    Johnson, Steven Hamilton, Tara Pandya, ``An Overview of New
    Monte Carlo Capabilities in SCALE: The Shift Monte Carlo Code,''
    2017 SCALE User's Group Workshop, Oak Ridge, TN., Sept. 27 (2017).
  \item Cole Gentry, Andrew Godfrey, Ben Collins, Tara Pandya, Greg
    Davidson, Fausto Franceschini, ``Shift Lattice Depletion / 2D
    Secondary Source Modeling Capability,'' The Consortium for
    Advanced Simulation of LWRs, Cranberry Meeting, June (2017).
  \item Lei Jin, Kaushik Banerjee, Steven Hamilton, Gregory
    Davidson, ``Variance Estimation in Monte Carlo Eigenvalue
    Simulations using Spectral Analysis Methods,'' American Nuclear
    Society Annual Meeting, San Francisco, CA, June (2017).
  \item Douglas E. Peplow, Mathew W. Swinney, Gregory G. Davidson,
    Andrew D. Nicholson, and Bruce W. Patton, ``Initial Modeling of
    Urban Search Measurements,'' American Nuclear Society Annual
    Meeting, San Francisco, CA, June (2017).
  \item Cole Gentry, Andrew Godfrey, Tara Pandya, Gregory Davidson,
    and Fausto Franceschini, ``AP1000 Benchmarking of VERA Neutronics
    Toolset,'' M\&C 2017, Jeju, South Korea, April (2017).
  \item Elliott Biondo, Gregory Davidson, Tom Evans, Steven
    Hamilton, Seth Johnson, Tara Pandya, ``Monte Carlo Capabilities:
    Shift,'' GAIN/EPRI Symposium, Jan. (2017).
  \item Andrew D. Nicholson, Douglas E. Peplow, Daniel E. Archer,
    Mathew W. Swinney, Michael J. Willis, William R. Ray, Gregory
    G. Davidson, ``Source Injection with Particle Transport
    Models,'' Source Injection Workshop, Livermore, CA, Dec. 6-7
    (2016).
  \item Steven Hamilton, Greg Davidson, Tom Evans, and Kaushik
    Banerjee, ``Accelerated Monte Carlo Fission Source Convergence
    with a Deterministic Fission Matrix Method,'' American Nuclear
    Society Annual Meeting, New Orleans, LA, June 14, (2016).
  \item Gregory G. Davidson, Tara M. Pandya, Aarno Isotalo, Seth
    R. Johnson, Thomas M. Evans, William Wieselquist, ``Nuclide
    Depletion Capabilities in the Shift Monte Carlo Code,''
    PHYSOR-2016, Sun Valley, ID, May (2016).
  \item Greg Davidson, Tom Evans, Steven Hamilton, Seth Johnson,
    Tara Pandya, ``Oak Ridge National Laboratory: Modeling and
    Simulation Capabilities,'' University of Michigan, Department of
    Nuclear Engineering and Radiological Sciences, Career Fair
    Kickoff Seminar, Oct. 22, (2015).
  \item Tom Evans, Greg Davidson, Steven Hamilton, Seth Johnson,
    Wayne Joubert, Tara Pandya, Stuart Slattery, ``Scalable
    Algorithms for Deterministic and Monte Carlo Radiation
    Transport,'' Kinetic Theory Workshop, Oak Ridge National
    Laboratory, Oak Ridge, TN, Oct. 22 (2015).
  \item Chris Baker, Greg Davidson, Thomas Evans, Steve Hamilton,
    Josh Jarrell, and Wayne Joubert, ``High Performance Radiation
    Transport Simulations: Preparing for Titan,'' SC2012, Salt Lake
    City, Ut, Nov. (2012).
  \item Zane W. Bell, Greg G. Davidson, Ed D'Azevedo, Thomas
    M. Evans, Wayne Joubert, John K. Munro, Jr., Dilip R. Patlolla,
    and Bogdan Vacaliuc, ``Python for Development of OpenMP and CUDA
    Kernels for Multidimensional Data,'' 2011 Symposium on
    Application Accelerators in High Performance Computing
    (SAAHPC-11), Knoxville, TN, Jul (2011).
  \item G.G. Davidson, T.M. Evans, R.N. Slaybaugh, and C.G. Baker,
    ``Massively Parallel Solutions to the k-Eigenvalue Problem,''
    American Nuclear Society, Annual Meeting, November 7-11, 2010, Las
    Vegas, N.V.
  \item G. Davidson and E.W. Larsen, ``An Unconditionally-Stable
    Finite-Element Transport Method Without Sweeps,'' American Nuclear
    Society, Annual Meeting, November 11-15, 2007, Washington, D.C.
  \item G. Davidson and T.S. Palmer, ``Finite-Element Particle
    Transport using Wachspress Rational Basis Functions,''
    Computational Science Graduate Fellowship, Annual Conference, June
    20-22, 2006, Washington, D.C., available at
    http://www.cs-pi.org/csgf/conf/2006/presentations/davidson.shtml.
  \item G. Davidson, J.D. Densmore, A.K. Prinja, and J.E. Morel,
    ``Asymptotically Correct Angular Distributions for Monte
    Carlo-Diffusion Interfaces,'' American Nuclear Socity, Annual
    Meeting, June 4-8, 2006, Reno, NV.
  \item G. Davidson and T.S. Palmer, ``Finite Element Transport Using
    Wachspress Rational Basis Functions on Quadrilaterals in Diffusive
    Regions,'' Palais des Papes, Avignon, France, September 12-15,
    2005.
  \item G.G. Davidson and T.S. Palmer, ``Finite Element Diffusion on
    Arbitrary Quadrilaterals using Rational Basis Functions,'' American
    Nuclear Society, Annual Meeting, November 17-21, 2002, Washington,
    D.C.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftsubheading{Posters}
\begin{enumerate}
   \item Elliott D. Biondo, Gregory G. Davidson, Thomas M. Evans,
     Steven P. Hamilton, Seth R. Johnson, Tara M. Pandya, Katherine
     E. Royston, Jose L. Salcedo-Perez, Stefano Tognini, ``Shift: A
     Monte Carlo Radiation Transport Code for Leadership-Class
     Supercomputer,'' (2020).
  \item Tseelmaa Byambaakhuu, Shane Hart, and Gregory G. Davidson,
    ``Investigating the Magnus Series in Coupled Transport-Depletion
    Problems,'' NESLS Student Post Presentation, Aug (2019).
  \item Katherine Royston, Elliott Biondo, Eva Davidson, Gregory
    Davidson, Thomas Evans, Steven Hamilton, Seth Johnson, Tara
    Pandya, Georgeta Radulescu, and Joel Risner, ``High Performance
    Computing Modeling and Simulation for Nuclear Energy,'' Aug (2019).
  \item Elliott D. Biondo, Thomas M. Evans, Gregory G. Davidson, and
    Steven P. Hamilton, ``Singular Value Decomposition of Monte Carlo
    Weight Window Distributions,'' 5th Annual ORPA Research Symposium,
    Aug. (2017).
  \item Kaushik Banerjee, Gregory Davidson, Steven Hamilton, Thomas
    Evans, Lei Jin, ``Development and Investigation of Advanced
    Monte Carlo Fission Source Convergence Acceleration
    Methodologies,'' SEED Project, Sep. (2016).
  \item Joel Risner, David Chandler, Charles Daily, Greg Davidson,
    Seth Johnson, and Tara Pandya, ``Transformational Capability for
    Integrated Analysis of the High Flux Isotope Reactor (HFIR)
    Irradiation Experiments and Isotope Production Using
    High-Fidelity Modeling and Simulation,'' LDRD Poster
    Presentation (2015).
  \item Greg Davidson, Thomas Evans, Steven Hamilton, Seth Johnson,
    and Tara Pandya, ``Shift: A Parallel Monte Carlo Radiation
    Transport Package,'' M\&C2015, Nashville, TN (2015). 
  \item Greg Davidson, Tara Pandya, Prashant Jain, Seth Johnson,
    David Chandler, and Josh Peterson, ``Advanced Modeling and
    Simulation to Support LEU Conversion of HFIR,'' LDRD Poster
    Presentation (2014).
  \item Joshua J. Jarrell, Thomas M. Evans, and Gregory G. Davidson,
    ``Discrete Ordinates Quadrature Selection for Reactor-Based
    Eigenvalue Problem,'' M\&C2013, Sun Valley, ID, May, (2013).
  \item Gregory G. Davidson and Thomas M. Evans, ``Denovo: A
    Massively Parallel, Three-Dimensional Deterministic Transport
    Code for Reactor and Radiation Shielding Applications,''
    Multiphysics Methods Workshop, Sunriver, OR, June 8-9 (2010).
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Activities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Member of the American Nuclear Society, 1998-Present
  \begin{itemize}
    \item Local American Nuclear Society Executive Committee 2016 - Present
    \item Mathematics and Computations Division Executive Committee, 2011-2014
    \item Co-chair of the Mathematics and Computations Division
      Publicity Committee. 
	\item Vice President of the Student Chapter at Oregon State
      University, 1999-2000.
  \end{itemize}
\item Attended the 2011 MeV Summer School: Reactor Physics,
  Computations, Validation, and Integration in Multiphysics Codes 
\item Attended the 2008 Accerators for Science and Engineering
  Applications: GPUs and Multicores summer school 
\item Member of the American Nuclear Society, 1998-Present
\item Graduate Senator of the Associated Students of Oregon State
  University, 2004-2006.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Programming Languages: C++, C , Python, Fortran 90
\item Code Libraries: C++ Standard Template Libraries, BOOST,
  Trilinos, Silo, HDF5 
\item Version Control Software: CVS, Subversion, Git, Mercurial
\item Documentation: LaTex, Doxygen, reStructuredText, Wiki markup
\item Analysis Software: Mathematica, Matlab, Maple
\item Scientific Software: AMP, MCNP, Scale, Attila, VESTA, Serpent
\item Office Software: MS Office, OpenOffice
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
